Nail: A practical interface generator for data formats

### 2014-04-30 paper/osdi14/design.tex

\subsection{Goals}
\paragraph{Internal Model.}
Nail grammars describe both the \emph{external format} and an \emph{internal representation} of a
protocol, as opposed to existing grammar languages describe only the former and leave it up to the programmer to
construct an internal representation, typically in the form of an abstract syntax tree.

>>>>

Nail's goals are to reduce programmer effort required to safely interact
with data formats.  In particular, this means:

\begin{itemize}

\item Using the grammar to define both the \emph{external format}
      and the \emph{internal representation}.

\item Both parsing inputs into internal representations, as well as
      generating outputs from internal representations, without
      requiring the programmer to write any semantic actions.

\item Eliminating redundancy in internal representations, such as
      storing both an explicit length field and an implicit length
      of a container data structure, to ensure that programmers
      see a consistent view of the data.

\item Allow programmers to define grammars for complex real-world
      data formats through well-defined extensibility mechanisms.

\end{itemize}

\subsection{Overview}

\paragraph{Internal Model.}
Nail grammars describe both the \emph{external format} and an \emph{internal representation} of a
protocol, as opposed to existing grammar languages describe only the former and leave it up to the programmer to
construct an internal representation, typically in the form of an abstract syntax tree.
